Bayesian Sparsification of $\cplx$-valued networks

### 2019-11-08 paper/paper.tex
fixed indentation, and shortened cplx-vd

% The roles of $\Gamma$ and $C$ is more evident in univariate case: here $

@@

Let $(\mu_i)_{i=1}^m \in \cplx$ and $

@@

$ iid. Then $W = \sum_i \lvert \theta_i + z_i \rvert^2$ has a non-central $\chi^2_{2m}$
distribution with non-centrality parameter $s^2 = \sum_i \lvert \theta_i \rvert^2$. The
log-moments of $W$ for general integer $m \geq1$ are given in
\cite[p.~2466]{lapidoth_capacity_2003}.  % in fact Appendix X, Lemma 10.1

@@

@@

$ on $x < 0$, asymptotically $
  \log{(-x)} - \gamma
$ as $x\to 0-$ and $

@@

$ on $x \in (-\infty, -1]$ ($\gamma$ is Euler's constant).

@@

After cancellation \eqref{eq:var-do-kl-div-raw} becomes

@@

@@

% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (dubious)
Gradient-based methods that optimize \eqref{eq:elbo} usually do not rely on the value
of the objective. Since $\mathop{Ei}$ has simple analytic derivative and downstream
computations depend \eqref{eq:var-do-kl-div} only additively in\eqref{eq:elbo}, it is
possible to backpropagate through the divergence without forward evaluation.

>>>>

% The roles of $\Gamma$ and $C$ are more evident in univariate case: here $

@@

Let $

@@

$ iid and $\theta \in \cplx^m$. Then $
  W
    = \sum_i \lvert \theta_i + z_i \rvert^2
    \sim \chi^2_{2m}(s^2)
$ with $
  s^2 = \sum_i \lvert \theta_i \rvert^2
$, i.e. non-central $\chi^2_{2m}$ with parameter $s^2$. The log-moments
of $W$ for general integer $m \geq1$ are given in \cite[p.~2466]{lapidoth_capacity_2003}.
% in fact Appendix X, Lemma 10.1

@@

$, $

@@

$, $
  \mathop{Ei}(x) \approx \log{(-x)} - \gamma
$ (Euler's constant) as $x\to 0-$ and $

@@

$ on $x \in (-\infty, -1]$.

@@

Through \eqref{eq:expect-improper-term-cplx} and \eqref{eq:log-moment-for-chi-2} we get

@@

      \tag{\ref{eq:var-do-kl-div-raw}'} \,.

@@

% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (need proof)
Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
on \eqref{eq:var-do-kl-div}, it is possible to backpropagate through the divergence without
forward evaluation.
% Gradient-based optimiziation of \eqref{eq:elbo} usually does not use the value of the objective.
